Malacology: A Programmable Storage System

### 2017-03-08 paper/2_application_specific_storage_stacks.tex
popper: add source links to graphs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[ht]
\centering
\includegraphics{figures/obj-int-dev-growth.png}
\caption{Since 2010, the growth in the number of co-designed object storage
interfaces in Ceph has been accelerating. This plot is the number of object
classes (a group of interfaces), and the total number of methods (the actual
API end-points).}
\label{fig:obj-int-dev-growth}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\includegraphics{figures/obj-int-dev-growth.png}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/blob/v2.1/experiments/objclass-dev/visualize.ipynb}{source}]
Since 2010, the growth in the number of co-designed object storage interfaces
in Ceph has been accelerating. This plot is the number of object classes (a
group of interfaces), and the total number of methods (the actual API
end-points).} \label{fig:obj-int-dev-growth}
\end{figure}

### 2017-03-08 paper/6_evaluation.tex
popper: add source links to graphs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tbp]
\centering
\includegraphics{figures/capdelay-quota-behavior-a.png}
\includegraphics{figures/capdelay-quota-behavior-b.png}
\includegraphics{figures/capdelay-quota-behavior-c.png}
\caption{Each dot is an individual request, spread randomly along the \(y\)
axis. The default behavior is unpredictable, ``delay" lets clients hold the
lease longer, and ``quota" gives clients the lease for a number of operations.}
\label{fig:capdelay-quota-behavior}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics{figures/tradeoff.png}
\caption{Sequencer throughput by re-using various services.  The highest
performance is achieved using a single client with exclusive, cacheable
privilege. Round-robin sharing of the sequencer resource is affected by the
amount of time the resource is held, with best-effort performing the worst.}
\label{fig:captp}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics{figures/caps-delay-latency.png}
\caption{ The latency distribution shows that if the clients hold their
capabilities longer, performance decreases. Changing the delay can help the
sequencer and clients strike a balance between throughput and latency.}
\label{fig:capcdf}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=60mm,trim={1 4 4 1.3cm},clip]{figures/iface-update-delay.pdf}
\caption{Cluster-wide interface update latency, excluding the Paxos proposal cost for
interface commit.}
\label{fig:propdelay}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-behaviors.png}
\caption{CephFS/Mantle load balancing have better throughput than co-locating
all sequencers on the same server.  Sections~\ref{sec:feature-balancing-modes}
and~\ref{sec:feature-migration-units} quantify this improvement;
Section~\ref{sec:feature-backoff} examines the migration at 0-60 seconds.
}\label{fig:mantle-balancer-behaviors}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-performance.png}
\includegraphics{figures/mantle-mode-performance.png}
\caption{In (a) all CephFS balancing modes have the same performance; Mantle
uses a balancer designed for sequencers. In (b) the best combination of mode
and migration units can have up to a 2\(\times\)
improvement.}\label{fig:mantle-balancer-performance}
\end{figure}

@@

Using Mantle, the administrator can put the load balancer into ``proxy mode" or
``client mode". In proxy mode one server receives all requests and farms off
the requests to slave servers; the slave servers do the actual tail finding
operation. In client mode, clients interact directly with the server that has
their sequencer.  These modes are illustrated in Figure~\ref{fig:mantle-modes}.
``No Balancing" is when all sequencers are co-located on one physical server --
performance for that mode is shown by the ``No Balancing" curve in
Figure~\ref{fig:mantle-balancer-behaviors}. In ``Proxy Mode", clients continue
sending requests to server A even though some of the sequencers have been
migrated to another server. Server A redirects client requests for sequencer 2
to server B.  ``Proxy Mode (Half)" is shown in
Figure~\ref{fig:mantle-balancer-beahviors}; in this scenario, half of the
sequencers have migrated off the first server. Alternatively, ``Proxy Mode
(Full)", which is not pictured, is when all the sequencers migrate off the
first server.  ``Client Mode", shown on the far right of
Figure~\ref{fig:mantle-modes}, shows how clients for sequencer 2 contact server
B without a redirect from server A.

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-behavior.png}
\caption{The performance of proxy mode achieves the highest throughput but at
the cost of lower throughput for one of the sequencers. Client mode is more
fair but results in lower cluster throughput.
}\label{fig:mantle-mode-behavior}
\end{figure}

@@

This code snippet uses globally defined variables and tables from the Mantle
API~\ref{sevilla:sc15-mantle} to send half of the load on the current server (whoami) to the next ranked
server (whoami + 1); the \texttt{targets} array is a globally defined table
that the balancer uses to do the migrations. Alternatively, to migrate all load
a time step, we can remove the division by 2.

>>>>

\begin{figure}[tbp]
\centering
\includegraphics{figures/capdelay-quota-behavior-a.png}
\includegraphics{figures/capdelay-quota-behavior-b.png}
\includegraphics{figures/capdelay-quota-behavior-c.png}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/blob/v2.1/experiments/mds-zlog-seq-thruput-v-latency/results-reqdots-kill0-sameclient-capdelay-100-quota-100000/visualize.ipynb}{source}]
Each dot is an individual request, spread randomly along the \(y\) axis. The
default behavior is unpredictable, ``delay" lets clients hold the lease longer,
and ``quota" gives clients the lease for a number of operations.}
\label{fig:capdelay-quota-behavior}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics{figures/tradeoff.png}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/blob/v2.1/experiments/zlog-seqr-redux/viz.ipynb}{source}]
Sequencer throughput by re-using various services.  The highest performance is
achieved using a single client with exclusive, cacheable privilege. Round-robin
sharing of the sequencer resource is affected by the amount of time the
resource is held, with best-effort performing the worst.}
\label{fig:captp}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics{figures/caps-delay-latency.png}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/blob/v2.1/experiments/zlog-seqr-redux/viz.ipynb}{source}]
The latency distribution shows that if the clients hold their capabilities
longer, performance decreases. Changing the delay can help the sequencer and
clients strike a balance between throughput and latency.}
\label{fig:capcdf}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=60mm,trim={1 4 4 1.3cm},clip]{figures/iface-update-delay.pdf}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/tree/v2.1/experiments/mon-paxos-update/viz.py}{source}]
Cluster-wide interface update latency, excluding the Paxos proposal cost for
interface commit.}
\label{fig:propdelay}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-behaviors.png}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/blob/v2.1/experiments/mds-zlog-seq-migrate-redux-3client/results-mantle-runs/visualize.ipynb}{source}]
CephFS/Mantle load balancing have better throughput than co-locating all
sequencers on the same server.  Sections~\ref{sec:feature-balancing-modes}
and~\ref{sec:feature-migration-units} quantify this improvement;
Section~\ref{sec:feature-backoff} examines the migration at 0-60 seconds.
}\label{fig:mantle-balancer-behaviors}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-performance.png}
\includegraphics{figures/mantle-mode-performance.png}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/blob/v2.1/experiments/mds-zlog-seq-migrate-redux-3client/results-mantle-runs/visualize.ipynb}{source},
\href{https://github.com/michaelsevilla/malacology-popper/blob/v2.1/experiments/mds-zlog-seq-migrate-redux-waves/results-paper/visualize.ipynb}{source}]
In (a) all CephFS balancing modes have the same performance; Mantle uses a
balancer designed for sequencers. In (b) the best combination of mode and
migration units can have up to a 2\(\times\)
improvement.}\label{fig:mantle-balancer-performance}
\end{figure}

@@

Using Mantle, the administrator can put the load balancer into ``proxy mode" or
``client mode". In proxy mode one server receives all requests and farms off
the requests to slave servers; the slave servers do the actual tail finding
operation. In client mode, clients interact directly with the server that has
their sequencer.  These modes are illustrated in Figure~\ref{fig:mantle-modes}.
``No Balancing" is when all sequencers are co-located on one physical server --
performance for that mode is shown by the ``No Balancing" curve in
Figure~\ref{fig:mantle-balancer-behaviors}. In ``Proxy Mode", clients continue
sending requests to server A even though some of the sequencers have been
migrated to another server. Server A redirects client requests for sequencer 2
to server B.  ``Proxy Mode (Half)" is shown in
Figure~\ref{fig:mantle-balancer-behaviors}; in this scenario, half of the
sequencers have migrated off the first server. Alternatively, ``Proxy Mode
(Full)", which is not pictured, is when all the sequencers migrate off the
first server.  ``Client Mode", shown on the far right of
Figure~\ref{fig:mantle-modes}, shows how clients for sequencer 2 contact server
B without a redirect from server A.

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-behavior.png}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/blob/v2.1/experiments/mds-zlog-seq-migrate-redux-waves/results-paper/visualize.ipynb}{source}]
The performance of proxy mode achieves the highest throughput but at the cost
of lower throughput for one of the sequencers. Client mode is more fair but
results in lower cluster throughput.  }\label{fig:mantle-mode-behavior}
\end{figure}

@@

This code snippet uses globally defined variables and tables from the Mantle
API~\cite{sevilla:sc15-mantle} to send half of the load on the current server (whoami) to the next ranked
server (whoami + 1); the \texttt{targets} array is a globally defined table
that the balancer uses to do the migrations. Alternatively, to migrate all load
a time step, we can remove the division by 2.
